A Framework for Predictable Actor-Critic Control

### 2022-05-07 documentation/paper.tex
-

\documentclass{article}
\usepackage{neurips_2022} % for first submission 
% \usepackage[preprint]{neurips_2022}
% \usepackage[final]{neurips_2022}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors

\title{FIXME}
\author{%
    Jeff Hykin
    \texttt{hippo@cs.cranberry-lemon.edu} \\
    % examples of more authors
    % \And
    % Coauthor \\
    % Affiliation \\
    % Address \\
    % \texttt{email} \\
    % \AND
    % Coauthor \\
    % Affiliation \\
    % Address \\
    % \texttt{email} \\
    % \And
    % Coauthor \\
    % Affiliation \\
    % Address \\
    % \texttt{email} \\
    % \And
    % Coauthor \\
    % Affiliation \\
    % Address \\
    % \texttt{email} \\
}

@@

>>>>

\documentclass{article}
\usepackage{neurips_2022} % for first submission 
% \usepackage[preprint]{neurips_2022}
% \usepackage[final]{neurips_2022}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
% custom
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}

\title{A Framework for Predictable Actor-Critic Control}
\author{%
    % Josiah Coad, \textsuperscript{\rm 1}
    % Jeff Hykin, \textsuperscript{\rm 2}
    % James Ault, \textsuperscript{\rm 2}
    % Guni Sharon \textsuperscript{\rm 2}
    Jeff Hykin
    \texttt{hippo@cs.cranberry-lemon.edu} \\
    % examples of more authors
    % \And
    % Coauthor \\
    % Affiliation \\
    % Address \\
    % \texttt{email} \\
    % \AND
    % Coauthor \\
    % Affiliation \\
    % Address \\
    % \texttt{email} \\
    % \And
    % Coauthor \\
    % Affiliation \\
    % Address \\
    % \texttt{email} \\
    % \And
    % Coauthor \\
    % Affiliation \\
    % Address \\
    % \texttt{email} \\
}

@@

    % 
    % epsilon optimizer
    % 
    \begin{algorithm}[h]
        % \SetAlgoLined\
        \SetKwInOut{Input}{Input}
        \SetKwInOut{Output}{Output}
        \Input{
            multiplier for epsilon $\mathrm{inc}$,\\
            baseline min confidence interval $\mathrm{b_{min}}$,\\
            confidence interval $\mathrm{ci_{lvl}}$,\\
            minimum average episode reward $\mathrm{b_{lower}}$,\\
            baseline confidence interval width $\mathrm{b_{ci}}$,\\
            number of baseline samples $\mathrm{b_{sz}}$,\\
            initial epsilon $\mathrm{\epsilon_{i}}$,\\
            initial horizon $\mathrm{h_{i}}$,\\
            number of iterations of refinement $\mathrm{iter}$\\    
        }
        \Output{
            \\
            a refined epsilon $\mathrm{\epsilon_{i}}$
            a refined horizon $\mathrm{h_{i}}$
        }
        \caption{Refine2}
        \label{algo:replan2}

        Initialize an empty array $ epsilon\_attempts $
        Initialize an empty hash map $ planlens_\epsilon $. Requesting a non-existent key for $ planlens_\epsilon $ returns an array containing $h_i$

        \For{$i$ in $[0,..., iter]$}{
            \label{ln:loopplan1}
            Initialize an empty array $sampled\_rewards$ 
            $a \gets 10$ 
            \For{$i$ in $[0,..., b_{sz}]$}{
                \label{ln:loopsample1}
                $discounted\_rewards, planlens 
                    \gets run\_episode(\epsilon=e_n)$ 
                $sampled\_rewards.push(\sigma(discounted\_rewards))$ 
                $planlens_\epsilon[\epsilon\_n] 
                    \gets concat(planlens_\epsilon[\epsilon_i], planlens)$

                \If{$length(sampled\_rewards) < 2$} {
                    $continue$
                }

                $s_{max}           \gets
                \hspace{0.5cm}    confidence\_interval\_upper(ci_{lvl}, sampled\_rewards)$
                $confidence\_size \gets
                \hspace{0.5cm}    confidence\_interval\_size(ci_{lvl} , sampled\_rewards)$
                \If{$s_{max} < baseline_{min} \leq confidence_size < b_ci$}{
                    $break$
                }
            }

            \If{$mean(sampled\_rewards) \geq b_{lower}$}{
                $\epsilon_n \*= inc$
            }{
                $\epsilon_n \/= inc$
            }

            $epsilon\_attempts.push(\epsilon_n)$
        }
        $\epsilon_o = median(epsilon\_attempts)$

        $h_o = max(median(planlens_\epsilon[\epsilon_o]), 1) * 2$

        \Return{
            $\mathrm{\epsilon_{o}}$
            $\mathrm{h_{o}}$
        }
    \end{algorithm}
